Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.

### 2017-08-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
latest updates

\title{ \blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}}

@@

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
 Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods \sep Capillary number.
\end{keyword}

>>>>

\title{ Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}

@@

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
 Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio \sep Preferential flowpath \sep Finite Element Methods \sep Capillary number \sep Unstructured domain \sep Mesh adaptivity.
\end{keyword}
